BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-12 introduction.tex
Joe Section Added

\paragraph{Contributions.}The core contribution of my thesis is the design and implementation of BlueTracer, a robust library and system call tracer for Windows programs specialized in evasive malware.

@@

We first validated BlueTracer on benign applications exercising a large number of functions, and then on a popular security product used for assessing how stealthy a malware analysis system is against a large body of public evasion techniques used in the wild. The obtained results suggested that BlueTracer can be very effective in tracing a malware sample's activities while remaining undetected. 
\iffalse
I then analyzed a set of highly evasive samples collected by Joe Security, the proclaimed technology leader for the analysis of evasive malware, as they feature exotic evasions that most analysis products have struggled to deal with. The logs collected by BlueTracer reveal behaviors consistent with the analysis reports authored by Joe Security, suggesting that BlueTracer can be very effective in tracing a malware sample's activities while remaining undetected. 
\fi

\paragraph{Structure of the Thesis.}
The remaining part of this thesis is structured as follows.
Chapter \ref{background} describes the major \textit{API hooking} techniques present in literature, outlining their stengths and weaknesses, especially from a detection point of view. It also introduces the concept of Dynamic Binary Instrumentation (DBI), which constitutes BlueTracer's core.
Chapter \ref{implementation} focuses on the implementation of the tool, on its structure and the design choices which were made during its development.
Chapter \ref{conclusion} illustrates the experimental results and assesses the tool's effectiveness.
Finally, we present concluding remarks in Chapter 5, together with possible future developments.

>>>>

\subsubsection{Contributions}
The core contribution of my thesis is the design and implementation of BlueTracer, a robust library and system call tracer for Windows programs specialized in evasive malware.

@@

We first validated BlueTracer on benign applications exercising a large number of functions, and then on a popular security product used for assessing how stealthy a malware analysis system is against a large body of public evasion techniques used in the wild. We then analyzed a set of highly evasive samples collected by Joe Security \cite{JoeBox}, the proclaimed technology leader for the analysis of evasive malware, as they feature exotic evasions that most analysis products have struggled to deal with. The logs collected by BlueTracer reveal behaviors consistent with the analysis reports authored by Joe Security, suggesting that BlueTracer can be very effective in tracing a malware sample’s activities while remaining undetected. 
\iffalse
I then analyzed a set of highly evasive samples collected by Joe Security, the proclaimed technology leader for the analysis of evasive malware, as they feature exotic evasions that most analysis products have struggled to deal with. The logs collected by BlueTracer reveal behaviors consistent with the analysis reports authored by Joe Security, suggesting that BlueTracer can be very effective in tracing a malware sample's activities while remaining undetected. 
\fi

%\paragraph{Structure of the Thesis.}
\subsubsection{Structure of the Thesis}
The remaining part of this thesis is structured as follows.
Chapter \ref{background} describes the major \textit{API hooking} techniques present in literature, outlining their stengths and weaknesses, especially from a detection point of view. It also introduces the concept of Dynamic Binary Instrumentation (DBI), which constitutes BlueTracer's core.
Chapter \ref{implementation} focuses on the implementation of the tool, on its structure and the design choices which were made during its development.
Chapter \ref{conclusion} illustrates the experimental results and assesses the tool's effectiveness.
Finally, we present concluding remarks in Chapter 5, together with possible future developments.
